### 2018-09-23 ApproxComp/TKDE/sec-beyond.tex

We have seen that data sampling helps to achieve a balance between efficiency and effectiveness for link prediction,
and other techniques such as incremental computation, data partitioning, data indexing and distributed computing can
also be unitized for big data analytics, and even for designing query and data approximation techniques for big data analytics.
For instance, it is easy to see that incremental algorithms (see~\cite{Reps96} for a survey) can be utilized to achieve query approximation.

It is also obvious that techniques beyond query approximation and data approximation, such as theory and systems~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}, are must things for big data analytics.

>>>>

We have seen that sampling helps to achieve a balance between efficiency and effectiveness for approximate query processing~\cite{ChaudhuriDK17,Mozafari17,Kraska17,GarofalakisG01} and link prediction~\cite{DuanAMHH16,DuanMAMH17}},
and other techniques such as incremental computation~\cite{Reps96,FanLMTWW10,rankicde2018}, distributed computing~\cite{MaCHW12,FanXWYJZZCT17}, and system techniques~\eg caching~\cite{WangLMNT18}, new hard ware~\cite{ArulrajPD15,iccd2018} can also be unitized for big data analytics, and can even be combined for designing query and data approximation techniques for big data analytics.

It is worth pointing out that for all kind of techniques big data analytics, various computing resources should be seriously considered, \eg using bounded resources for approximation~\cite{CaoF17} and for incremental computation~\cite{abs-1801-01012}. It is also obvious that techniques beyond query approximation and data approximation, such as theory and systems~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}, are must things for big data analytics.

### 2018-09-23 ApproxComp/TKDE/sec-conclusion.tex

In this article we have systematiclly introduced approximation computation techniques for efficient and effective big data analytics.
Furthermore, although approximate computation does not put
theoretical bounds with respect to optimal solutions, it does expect a balance between efficiency and effectiveness. Indeed, (a) our query approximation techniques~\cite{tods-MaCFHW14,LinMZWH17,MaHWLH17} show that efficiency can be obtained with high accuracy in practice, and (b) our data approximation techniques for shortest paths/distances and link prediction~\cite{MaFLWCH16,DuanMAMH17} show that efficiency and accuracy can be obtained simultaneously for certain data analytic tasks. That is, the design policy of approximate computation is not to sacrifice effectiveness for efficiency, but to achieve both efficiency and effectiveness in practice.

>>>>

In this article we have systematiclly introduced approximation computation techniques for efficient and effective big data analytics.
Furthermore, although approximate computation does not put
theoretical bounds with respect to optimal solutions, it does expect a balance between efficiency and effectiveness. Indeed, (a) our query approximation techniques~\cite{ShuaiMaVLDB12,tods-MaCFHW14,LinMZWH17,MaHWLH17} show that efficiency can be obtained with high accuracy in practice, and (b) our data approximation techniques for shortest paths/distances and link prediction~\cite{MaFLWCH16,MaFLWCH17,HuAMH16,DuanAMHH16,DuanMAMH17} show that efficiency and accuracy can be obtained simultaneously for certain data analytic tasks. That is, the design policy of approximate computation is not to sacrifice effectiveness for efficiency, but to achieve both efficiency and effectiveness in practice.

### 2018-09-23 ApproxComp/TKDE/sec-data.tex

Essentially, in our graph embedding, $d$ represents the number of communities. As the anomalous nodes are only determined by influential communities and nodes typically connect to a limited number of communities, the complete d-dimensions are unnecessary, and a limited number of communities suffice to ascertain anomalies. Thus, our dimension reduction technique (referred to as ($k+\beta$ reduction) only maintains ($k + \beta$)-dimensions for embedding of each node, where k is the maximum number of communities to connect, $\beta$ is to tolerate mistakes when determining the $k$ communities and is removed after the computation process. Here $k \ll d$ and  $\ll d$, \eg $k = 10$ and $\beta = 2$ and $d=600$ for a network with $10^6$ nodes.

Using both real-life data and synthetic
data , we conduct an extensive experimental study.
 (a) The modularity \cite{newman1} was increased about 4.9\% and 3.6\% with our approach and oddball~\cite{akoglu14}, respectively; (b) The $F_1$ measure was about $88\%$ and $70\%$ for synthetic with our approach and oddball, respectively; (c) The running time of our embedding approach increases reasonably with the increase of graph sizes, even with large number of communities, while traditional  multidimensional scaling approach~\cite{mds} ran out of memory.

>>>>

Essentially, in our graph embedding, $d$ represents the number of communities. As the anomalous nodes are only determined by influential communities and nodes typically connect to a limited number of communities, the complete d-dimensions are unnecessary, and a limited number of communities suffice to ascertain anomalies. Thus, our dimension reduction technique (referred to as ($k+\beta$ reduction) only maintains ($k + \beta$)-dimensions for embedding of each node, where k is the maximum number of communities to connect, $\beta$ is to tolerate mistakes when determining the $k$ communities and is removed after the computation process. Here $k, \beta \ll d$, \eg $k = 10$ and $\beta = 2$ and $d=600$ for a network with $10^6$ nodes.

Using both real-life data and synthetic
data , we conduct an extensive experimental study.
 (a) The modularity \cite{newman1} was increased about 4.9\% and 3.6\% with our approach and OddBall~\cite{akoglu14}, respectively; (c) Our approach scales to graph graphs with large number of communities, while traditional  multidimensional scaling approach~\cite{mds} ran out of memory.

### 2018-09-23 ApproxComp/TKDE/sec-introduction.tex

Over the past a few years, research and development has made significant progresses on big data analytics with the supports from both governments and industries all over the world, such as Spark\footnote{\small \url{https://spark.apache.org}}, IBM Watson\footnote{\small \url{https://www.ibm.com/watson}} and Google AlphaGo\footnote{\small \url{https://deepmind.com/research/alphago}}. A fundamental issue for big data analytics is the efficiency, and various advances towards attacking this issues have been achieved recently, from theory to algorithms to systems~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}. However, if the optimal solution is unable to attain or not required or has a price to high to pay, it is reasonable to sacrifice optimality with a ``good'' feasible solution that can be computed efficiently. Hence, various approximation techniques have been developed, and can be classified into three aspects: algorithms, SQL aggregate queries and multiple layers of the system stack.
\bi
\item[(1)] {\em Approximation algorithms} were formalized in the 1970s~\cite{GareyGU72,Johnson74a}, and an approximation algorithm is necessarily polynomial, and is evaluated by the worst case possible relative error over all possible instances of the  NP-hard optimization problem, under the widely believed $P\ne NP$ conjecture. This is relatively mature research field algorithm community, many approximation algorithm have been designed for optimization problems~\cite{Dorit96,approx03,Ausiello99}.
\item[(2)] {\em Approximate query processing} supports a slightly constrained set of SQL-style declarative queries, and it specifically provides approximate results for standard SQL aggregate queries, \eg queries involving COUNT, AVG, SUM and PERCENTILE. Over the past two decades, approximate query processing has been successfully studied, among which sampling technique are heavily employed~\cite{ChaudhuriDK17,Mozafari17,Kraska17,GarofalakisG01}. There are not only classical DBMS systems such as Oracle that provide approximate functions to support approximate results~\footnote{\small \url{https://oracle-base.com/articles/12c/approximate-query-processing-12cr2}}, but also emerging new systems specially designed for approximate queries, such as BlinkDB~\footnote{\small \url{http://blindb.org/}}, Verdict~\footnote{\small \url{http://verdictdb.org/}}, Simba~~\footnote{\small \url{https://initialdlab.github.io/Simba/index.html}}. However, as pointed out in~\cite{ChaudhuriDK17}, `` it seems impossible to have an AQP system that supports the richness of SQL with significant saving of work while providing an accuracy guarantee that is acceptable to a broad set of application workloads.''

\item[(3)] {\em Approximation computing} is a recent computation technique that returns a possibly inaccurate result rather than a guaranteed accurate result from a system point of view.  It is involved with multiple layers of the system stack from software to hardware to systems (such as approximate circuits, approximate storage and loop perforation), and can be used for applications where an approximate result is sufficient for its purpose~\cite{AgrawalCGGNOPSS16,Mittal16b}. Recently, Workshop on approximate computing across the stack has been usefully held for research on hardware, programming languages and compiler support  for approximate computing  since 2014.  (2015~\footnote{\small \url{https://sampa.cs.washington.edu/new/wax2015/}},2016~\footnote{\small \url{http://approximate.computer/wax2016/}},2017~\footnote{\small  \url{http://approximate.computer/wax2017/}}, 2018~\footnote{\small  \url{http://approximate.computer/wax2018/}}). Besides the various task oriented quality metrics,  the quality-energy trade-off is also  concerned for approximate computing. For example, in k-means clustering algorithm, allowing only 5\% loss in classification accuracy can provide 50 times energy saving compared to the fully accurate classification~\cite{Mittal16b}
\ei

In this article, we present the idea of approximate computation for efficient and effective big data analytics: query approximation and data approximation, based on our recent research experiences. Different from existing approximation techniques~\cite{CormenLRS01,approx03,FanH14}, the approximation computation that we are going to introduce is unnecessarily theoretically bounded with respect to optimal solutions, but asks for both efficiency and effectiveness in practice.
????
\textbf{clarify differences
}
 is a computation which returns a possibly inaccurate result rather than a guaranteed accurate result, for a situation where an approximate result is sufficient for a purpose

>>>>

Over the past a few years, research and development has made significant progresses on big data analytics with the supports from both governments and industries all over the world, such as Spark\footnote{\small \url{https://spark.apache.org}}, IBM Watson\footnote{\small \url{https://www.ibm.com/watson}} and Google AlphaGo\footnote{\small \url{https://deepmind.com/research/alphago}}. A fundamental issue for big data analytics is the efficiency, and various advances towards attacking this issues have been achieved recently, from theory to algorithms to systems~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}. However, if the optimal solution is unable to attain or not required or has a price to high to pay, it is reasonable to sacrifice optimality with a ``good'' feasible solution that can be computed efficiently. Hence, various approximation techniques have been developed, and can be classified into three aspects: algorithms, SQL aggregate queries and multiple layers of the system stack.
\bi
\item[(1)] {\em Approximation algorithms} were formalized in the 1970s~\cite{GareyGU72,Johnson74a}, and an approximation algorithm is necessarily polynomial, and is evaluated by the worst case possible relative error over all possible instances of the  NP-hard optimization problem, under the widely believed $P\ne NP$ conjecture. This is relatively mature research field algorithm community, many approximation algorithm have been designed for optimization problems~\cite{Dorit96,approx03,Ausiello99}.
\item[(2)] {\em Approximate query processing} supports a slightly constrained set of SQL-style declarative queries, and it specifically provides approximate results for standard SQL aggregate queries, \eg queries involving COUNT, AVG, SUM and PERCENTILE. Over the past two decades, approximate query processing has been successfully studied, among which sampling technique are heavily employed~\cite{ChaudhuriDK17,Mozafari17,Kraska17,GarofalakisG01}. There are not only classical DBMS systems such as Oracle that provide approximate functions to support approximate results~\footnote{\small \url{https://oracle-base.com/articles/12c/approximate-query} \url{-processing-12cr2}}, but also emerging new systems specially designed for approximate queries, such as BlinkDB~\footnote{\small \url{http://blindb.org/}}, Verdict~\footnote{\small \url{http://verdictdb.org/}}, Simba~~\footnote{\small \url{https://initialdlab.github.io/Simba/index.html}}. However, as pointed out in~\cite{ChaudhuriDK17}, `` it seems impossible to have an AQP system that supports the richness of SQL with significant saving of work while providing an accuracy guarantee that is acceptable to a broad set of application workloads.''

\item[(3)] {\em Approximation computing} is a recent computation technique that returns a possibly inaccurate result rather than a guaranteed accurate result from a system point of view.  It is involved with multiple layers of the system stack from software to hardware to systems (such as approximate circuits, approximate storage and loop perforation), and can be used for applications where an approximate result is sufficient for its purpose~\cite{AgrawalCGGNOPSS16,Mittal16b}. Recently, workshop on approximate computing across the stack has been usefully held for research on hardware, programming languages and compiler support  for approximate computing  since 2014.  (2015~\footnote{\small \url{https://sampa.cs.washington.edu/new/wax2015/}},2016~\footnote{\small \url{http://approximate.computer/wax2016/}},2017~\footnote{\small  \url{http://approximate.computer/wax2017/}}, 2018~\footnote{\small  \url{http://approximate.computer/wax2018/}}). Besides the various task oriented quality metrics,  the quality-energy trade-off is also  concerned for approximate computing. For example, in k-means clustering algorithm, allowing only 5\% loss in classification accuracy can provide 50 times energy saving compared to the fully accurate classification~\cite{Mittal16b}
\ei

In this article, we present the idea of approximate computation for efficient and effective big data analytics: query approximation and data approximation, based on our recent research experiences~\cite{MaCHW12,ShuaiMaVLDB12,tods-MaCFHW14,LinMZWH17,MaHWLH17,MaFLWCH16,MaFLWCH17,HuAMH16,DuanAMHH16,DuanMAMH17,rankicde2018}.
Approximation algorithms ask for feasible solutions that are theoretically bounded with respect to optimal solutions from an algorithm design aspect.
Approximate query processing and approximation computing relax the need for accuracy guarantees for aggregate SQL queries and for multiple layers of the system stack, respectively. Similarly, our approximate computation is unnecessarily theoretically bounded with respect to optimal solutions, but from an algorithm design point of view. That is, we focus on approximate computation for big data analytics for a situation where an approximate result is sufficient for a purpose.

%Different from existing approximation techniques~\cite{CormenLRS01,approx03,FanH14}, the approximation computation that we are going to introduce is unnecessarily theoretically bounded with respect to optimal solutions, but asks for both efficiency and effectiveness in practice.
